Bipartite Fidelity and Loschmidt echo of bosonic conformal interface

### 2017-04-30 comp_fid_echo.tex
bCFT_paper restored, intro wasn't there but added manually. All the standalone figures are there, most likely
Merge branch 'master' of https://bitbucket.org/msgboxa/bcft_paper (reverted from commit 5385d6b0de3258810667564c8e0a53e008f8f561)

The Bogoliubov transformation that diagonalizes the Hamiltonian
\begin{eqnarray}\begin{aligned}
\label{Def. of a}
({\bf a} , {\bf a}^\dagger)\equiv({\bf b} , {\bf b}^\dagger)S
\end{aligned}\end{eqnarray}
should preserve the commutation relation
\begin{eqnarray}\begin{aligned}
\label{Preserve commutator}
J\equiv\left(\begin{array}{ccc}
0 & {\bf I}\\
-{\bf I} & 0
\end{array}\right)
=\left[
\left(\begin{array}{ccc}
{\bf a} \\
{\bf a}^\dagger
\end{array}\right),
\left(\begin{array}{ccc}
{\bf a} & {\bf a}^\dagger
\end{array}\right)\right]
=S^T\left[
\left(\begin{array}{ccc}
{\bf b} \\
{\bf b}^\dagger
\end{array}\right),
\left(\begin{array}{ccc}
{\bf b} & {\bf b}^\dagger
\end{array}\right)\right]S
=S^T JS,
\end{aligned}\end{eqnarray}
where the commutator, for example, $\left[{\bf b},{\bf b}^\dagger\right]$ is understood as a matrix with component $\left[b_i,b_j^\dagger\right]=\delta_{ij}$. It is clear from Eq.(\ref{Preserve commutator}) that $S\in$Sp(2N,{\bf C}){\bf\color{red}Cite sth}. Further, the requirement that $a^\dagger$ is a complex conjugation of $a$ leads to the block structure of S
\begin{eqnarray}\begin{aligned}
\label{Block of S}
S=\left(\begin{array}{ccc}
u & v^*\\
v & u^*
\end{array}\right).
\end{aligned}\end{eqnarray}
The symplectic property of S implies the following constraints 
\begin{eqnarray}
u^\dagger u-v^\dagger v&={\bf I}\label{Constraint 1}\\
u^T u-v^T v&=0\label{Constraint 2}
\end{eqnarray}
which will be important for calculation of the ground state.

@@

{\bf\color{red} 1. Comment of BCS; 2. Say sth of deferment of the discussion of how to find S explicitly; 3. }

@@

Fidelity is defined as the overlap of groundstates of two different bosonic Hamiltonians{\bf\color{red}cite sth}. We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in ${\bf b}$ basis, as in Eq.(\ref{Quadratic boson H}). From the discussion in App.{\bf\color{red}where}, we are able to diagonalize it in ${\bf a}$ basis. At $t=0$, the Hamiltonian becomes $\hat{H}_1$, which is still in ${\bf b}$ basis, but is diagonalized in a new ${\bf c}$ basis. The corresponding Bogoliubov transformations read
\begin{eqnarray}\begin{aligned}
\label{Two BdG}
({\bf b} , {\bf b}^\dagger)S_0=({\bf a} , {\bf a}^\dagger)\quad
({\bf b} , {\bf b}^\dagger)S_1=({\bf c} , {\bf c}^\dagger)
\end{aligned}\end{eqnarray}
such that
\begin{eqnarray}\begin{aligned}
\label{S0invS}
({\bf a} , {\bf a}^\dagger)S_0^{-1}S_1=({\bf c} , {\bf c}^\dagger)
\end{aligned}\end{eqnarray}
One immediately realizes Eq.(\ref{S0invS}) takes the same form as Eq.(\ref{Def. of a}) such that $S_0^{-1}S_1$ is in the same symplectic group, and takes the following block form
\begin{eqnarray}
S_0^{-1}S_1=\left(\begin{array}{ccc}
u_1 & v_1^*\\
v_1 & u_1^*
\end{array}\right).
\end{eqnarray}
Thus $|0\rangle_{\bf c}$ is related to the $|0\rangle_{{\bf a}}$ in the same way as in Eq.(\ref{Boson BCS gnd}), and their overlap, which is the fidelity, reads
\begin{eqnarray}\begin{aligned}
|_{\bf a}\langle0|0\rangle_{\bf c}|^2=\frac{1}{|\text{det}(u_1)|}
\end{aligned}\end{eqnarray}

@@

\subsection{Description on how to get S}

@@

We introduce the real basis 
\begin{eqnarray}\begin{aligned}
\label{Real basis}
\left(\begin{array}{ccc}
{\bf b}\\
{\bf b}^\dagger
\end{array}\right)
=C\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
=\frac{1}{\sqrt{2}}\left(\begin{array}{ccc}
1 & i \\
1 & -i
\end{array}\right)\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
\end{aligned}\end{eqnarray}
in which the Hamiltonian reads
\begin{eqnarray}\begin{aligned}
\hat{H}
&=\frac{1}{2}
\left(\begin{array}{ccc}
\phi & \pi
\end{array}\right)
\left(\begin{array}{ccc}
\text{Re}(H+\Delta) & -\text{Im}(H-\Delta)\\
\text{Im}(H+\Delta)& \text{Re}(H-\Delta) \\
\end{array}\right)
\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
=\frac{1}{2}
\left(\begin{array}{ccc}
\phi & \pi
\end{array}\right)
\mathcal{M}
\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
\end{aligned}\end{eqnarray}
It is not hard to realize $\mathcal{M}$ is real and symmetric. We shall further assume that $\mathcal{M}$ is positive definite, and from Williamson's theorem{\bf\color{red}cite sth} we have
\begin{eqnarray}\begin{aligned}
\mathcal{M}=\tilde{S}\left(\begin{array}{ccc}
d\\
&d
\end{array}\right)\tilde{S}^T
\end{aligned}\end{eqnarray}
where $\tilde{S}\in$Sp(2N,{\bf R}) and the diagonal matrix $d$ are positive eigenvalues of $iJ\mathcal{M}$. Thus we have
\begin{eqnarray}\begin{aligned}
\label{Diagonalization of M}
M=J(C^{-1})^T\tilde{S}C^TJ^{-1}\left(\begin{array}{ccc}
d\\
&-d
\end{array}\right)C\tilde{S}^TC^{-1}.
\end{aligned}\end{eqnarray}
Using the fact that $\tilde{S}$ is an element of real symplectic group and the explicit form of C-matrix, one can show that Eq.(\ref{Diagonalization of M}) is a similarity transformation, and $C\tilde{S}^TC^{-1}$, which takes the block form as in Eq.(\ref{Block of S}), is an element of complex symplectic group. Thus we identify 
\begin{eqnarray*}\begin{aligned}
S\equiv C\tilde{S}^TC^{-1}
\end{aligned}\end{eqnarray*}
as the desired Bogoliubov transformation that diagonalizes the Hamiltonian in Eq.(\ref{Quadratic boson H2}).

Notice in the above construction, we have assumed the Hamiltonian in the real basis to be positive definite. {\bf\color{red}This is not as restrictive as it may appear}, and in App.{\bf\color{red}where} we shall explicitly construct the matrix $\tilde{S}$ for the case of harmonic chain.
\subsection{Harmonic chain}

@@

In the real basis defined in Eq.(\ref{Real basis}), the Hamiltonian for 1D harmonic chain reads
\begin{eqnarray}\begin{aligned}
\hat{H}
=\frac{1}{2}
\left(\begin{array}{ccc}
\phi & \pi
\end{array}\right)
\mathcal{M}
\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
=\frac{1}{2}
\left(\begin{array}{ccc}
\phi & \pi
\end{array}\right)
\left(\begin{array}{ccc}
\mathcal{V} \\
& {\bf I}
\end{array}\right)
\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
\end{aligned}\end{eqnarray}
where $\mathcal{V}$ is real symmetric matrix that can be diagonalized as $\mathcal{V}=\mathcal{O}D^2\mathcal{O}^T$. We construct the following real symplectic matrix
\begin{eqnarray}\begin{aligned}
\tilde{S}\equiv\left(\begin{array}{ccc}
\mathcal{O}D^{1/2} \\
& \mathcal{O}D^{-1/2}
\end{array}\right)
\end{aligned}\end{eqnarray}
such that 
\begin{eqnarray}\begin{aligned}
\mathcal{M}=\tilde{S}\left(\begin{array}{ccc}
D \\ 
& D
\end{array}\right)
\tilde{S}^T
\end{aligned}\end{eqnarray}
in accordance with Williamson's theorem. Thus the second quantized Hamiltonian will be diagonalized as
\begin{eqnarray}\begin{aligned}
M=S^{-1}\left(\begin{array}{ccc}
D \\
& -D
\end{array}\right)S
\end{aligned}\end{eqnarray}
where the Bogoliubov transformation take the desired block form
\begin{eqnarray}\begin{aligned}
S&=C\tilde{S}C^{-1}
&=\left(\begin{array}{ccc}
O(D^{1/2}+D^{-1/2}) & O(D^{1/2}-D^{-1/2}) \\
O(D^{1/2}-D^{-1/2}) & O(D^{1/2}+D^{-1/2}) 
\end{array}\right)
\end{aligned}\end{eqnarray}

>>>>

The Bogoliubov transformation that diagonalizes the Hamiltonian
\begin{eqnarray}\begin{aligned}
\label{Def. of a}
({\bf a} , {\bf a}^\dagger)\equiv({\bf b} , {\bf b}^\dagger)S
\end{aligned}\end{eqnarray}
should preserve the commutation relation
\begin{eqnarray}\begin{aligned}
\label{Preserve commutator}
J\equiv\left(\begin{array}{ccc}
0 & {\bf I}\\
-{\bf I} & 0
\end{array}\right)
=\left[
\left(\begin{array}{ccc}
{\bf a} \\
{\bf a}^\dagger
\end{array}\right),
\left(\begin{array}{ccc}
{\bf a} & {\bf a}^\dagger
\end{array}\right)\right]
=S^T\left[
\left(\begin{array}{ccc}
{\bf b} \\
{\bf b}^\dagger
\end{array}\right),
\left(\begin{array}{ccc}
{\bf b} & {\bf b}^\dagger
\end{array}\right)\right]S
=S^T JS,
\end{aligned}\end{eqnarray}
where the commutator, for example, $\left[{\bf b},{\bf b}^\dagger\right]$ is understood as a matrix with component $\left[b_i,b_j^\dagger\right]=\delta_{ij}$. It is clear from Eq.(\ref{Preserve commutator}) that $S\in$Sp(2N,{\bf C})\cite{fulton_representation_2004}. Further, the requirement that $a^\dagger$ is a complex conjugation of $a$ leads to the block structure of S
\begin{eqnarray}\begin{aligned}
\label{Block of S}
S=\left(\begin{array}{ccc}
u & v^*\\
v & u^*
\end{array}\right).
\end{aligned}\end{eqnarray}
The symplectic property of S implies the following constraints 
\begin{eqnarray}
u^\dagger u-v^\dagger v&={\bf I}\label{Constraint 1}\\
u^T u-v^T v&=0\label{Constraint 2}
\end{eqnarray}
which will be important for calculation of the ground state.

@@

{\bf\color{red} 1. Comment of BCS; 2. Say sth of deferment of the discussion of how to find S explicitly; 3. We will see similar construction of BCS in fidelity and echo.}

@@

Fidelity is defined as the overlap of groundstates of two different bosonic Hamiltonians{\bf\color{red}cite sth}. We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in ${\bf b}$ basis, as in Eq.(\ref{Quadratic boson H}). From the discussion in App.{\bf\color{red}where}, we are able to diagonalize it in ${\bf a}$ basis. At $t=0$, the Hamiltonian becomes $\hat{H}_1$, which is still written in ${\bf b}$ basis, but is diagonalized in a new ${\bf c}$ basis. The corresponding Bogoliubov transformations read
\begin{eqnarray}\begin{aligned}
\label{Two BdG}
({\bf b} , {\bf b}^\dagger)S_0=({\bf a} , {\bf a}^\dagger)\quad
({\bf b} , {\bf b}^\dagger)S_1=({\bf c} , {\bf c}^\dagger)
\end{aligned}\end{eqnarray}
such that
\begin{eqnarray}\begin{aligned}
\label{S0invS}
({\bf a} , {\bf a}^\dagger)S_0^{-1}S_1=({\bf c} , {\bf c}^\dagger)
\end{aligned}\end{eqnarray}
One immediately realizes Eq.(\ref{S0invS}) takes the same form as Eq.(\ref{Def. of a}) such that $S_0^{-1}S_1$ is in the same symplectic group, and takes the following block form
\begin{eqnarray}
S_0^{-1}S_1=\left(\begin{array}{ccc}
u_1 & v_1^*\\
v_1 & u_1^*
\end{array}\right).
\end{eqnarray}
Thus $|0\rangle_{\bf c}$ is related to the $|0\rangle_{{\bf a}}$ in the same way as in Eq.(\ref{Boson BCS gnd}), and their overlap, which is the fidelity, reads
\begin{eqnarray}\begin{aligned}
|_{\bf a}\langle0|0\rangle_{\bf c}|^2=\frac{1}{|\text{det}(u_1)|}
\end{aligned}\end{eqnarray}

@@

\subsection{Explicit construction of symplectic Bogoliubov transformation}

@@

We introduce the real basis 
\begin{eqnarray}\begin{aligned}
\label{Real basis}
\left(\begin{array}{ccc}
{\bf b}\\
{\bf b}^\dagger
\end{array}\right)
=C\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
=\frac{1}{\sqrt{2}}\left(\begin{array}{ccc}
1 & i \\
1 & -i
\end{array}\right)\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
\end{aligned}\end{eqnarray}
in which the Hamiltonian reads
\begin{eqnarray}\begin{aligned}
\hat{H}
&=\frac{1}{2}
\left(\begin{array}{ccc}
\phi & \pi
\end{array}\right)
\left(\begin{array}{ccc}
\text{Re}(H+\Delta) & -\text{Im}(H-\Delta)\\
\text{Im}(H+\Delta)& \text{Re}(H-\Delta) \\
\end{array}\right)
\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
=\frac{1}{2}
\left(\begin{array}{ccc}
\phi & \pi
\end{array}\right)
\mathcal{M}
\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
\end{aligned}\end{eqnarray}
It is not hard to realize $\mathcal{M}$ is real and symmetric. We shall further assume that $\mathcal{M}$ is positive definite, and from Williamson's theorem{\bf\color{red}cite sth} we have the decomposition
\begin{eqnarray}\begin{aligned}
\mathcal{M}=\tilde{S}\left(\begin{array}{ccc}
d\\
&d
\end{array}\right)\tilde{S}^T
\end{aligned}\end{eqnarray}
where $\tilde{S}\in$Sp(2N,{\bf R}) and the diagonal matrix $d$ are positive eigenvalues of $iJ\mathcal{M}$. Thus we have
\begin{eqnarray}\begin{aligned}
\label{Diagonalization of M}
M=J(C^{-1})^T\tilde{S}C^TJ^{-1}\left(\begin{array}{ccc}
d\\
&-d
\end{array}\right)C\tilde{S}^TC^{-1}.
\end{aligned}\end{eqnarray}
Using the fact that $\tilde{S}$ is an element of real symplectic group and the explicit form of C-matrix, one can show that Eq.(\ref{Diagonalization of M}) is a similarity transformation, and $C\tilde{S}^TC^{-1}$, which takes the block form as in Eq.(\ref{Block of S}), is an element of complex symplectic group. Thus we identify 
\begin{eqnarray*}\begin{aligned}
S\equiv C\tilde{S}^TC^{-1}
\end{aligned}\end{eqnarray*}
as the desired Bogoliubov transformation that diagonalizes the Hamiltonian in Eq.(\ref{Quadratic boson H2}).

Notice in the above construction, we have assumed the Hamiltonian $\mathcal{M}$ in the real basis to be positive definite. It is not hard find such a system, for example a harmonic chain, that meets the assumption. We shall explicitly construct the matrix $\tilde{S}$ for the case of harmonic chain in App.{\bf\color{red}where}.
\subsection{Harmonic chain}

@@

In the real basis defined in Eq.(\ref{Real basis}), the Hamiltonian for 1D harmonic chain reads
\begin{eqnarray}\begin{aligned}
\hat{H}
=\frac{1}{2}
\left(\begin{array}{ccc}
\phi & \pi
\end{array}\right)
\mathcal{M}
\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
=\frac{1}{2}
\left(\begin{array}{ccc}
\phi & \pi
\end{array}\right)
\left(\begin{array}{ccc}
\mathcal{V} \\
& {\bf I}
\end{array}\right)
\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
\end{aligned}\end{eqnarray}
where $\mathcal{V}$ is real symmetric matrix that can be diagonalized as $\mathcal{V}=\mathcal{O}D^2\mathcal{O}^T$. The explicit form of $\mathcal{V}$ depends on the boundary condition which is not important in the following construction. We define the following real symplectic matrix
\begin{eqnarray}\begin{aligned}
\tilde{S}\equiv\left(\begin{array}{ccc}
\mathcal{O}D^{1/2} \\
& \mathcal{O}D^{-1/2}
\end{array}\right)
\end{aligned}\end{eqnarray}
such that 
\begin{eqnarray}\begin{aligned}
\mathcal{M}=\tilde{S}\left(\begin{array}{ccc}
D \\ 
& D
\end{array}\right)
\tilde{S}^T
\end{aligned}\end{eqnarray}
in accordance with Williamson's theorem. Thus the second quantized Hamiltonian will be diagonalized as
\begin{eqnarray}\begin{aligned}
M=S^{-1}\left(\begin{array}{ccc}
D \\
& -D
\end{array}\right)S
\end{aligned}\end{eqnarray}
where the Bogoliubov transformation take the desired block form
\begin{eqnarray}\begin{aligned}
S&=C\tilde{S}C^{-1}
&=\left(\begin{array}{ccc}
O(D^{1/2}+D^{-1/2}) & O(D^{1/2}-D^{-1/2}) \\
O(D^{1/2}-D^{-1/2}) & O(D^{1/2}+D^{-1/2}) 
\end{array}\right)
\end{aligned}\end{eqnarray}

### 2017-04-30 gnd_dn_lambda.tex
bCFT_paper restored, intro wasn't there but added manually. All the standalone figures are there, most likely
Merge branch 'master' of https://bitbucket.org/msgboxa/bcft_paper (reverted from commit 5385d6b0de3258810667564c8e0a53e008f8f561)

\begin{figure}[h]
\centering
\includegraphics{fig_gnd_dn_lambda.pdf}
\caption{Partition function of Hamiltonian with DN and $\lambda$ boundary conditions. The width of the strip is $\pi$ due to folding. We unfold the cylinder and the new stripe have $N$ and $D$ boundary conditions on the left and right plus a $\lambda$ junction in the middle. }
\end{figure}

{\bf Eigenfunction}:

The unfolded configuration has D/N boundary conditions at $x = \pm \frac{L}{2}$ and linking boundary condition at $x = 0$. The general solutions can be written as
\begin{equation}
f(k, x) = 
\left\lbrace
\begin{aligned}
  A_1 e^{i kt} \cos(kx +\frac{1}{2}kL ) &  \quad x < 0  \\
  A_2 e^{ikt}  \sin(kx - \frac{1}{2}kL ) & \quad x > 0   \\
\end{aligned} \right. 
\end{equation}
At the junction we have $\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2}$, which cancels the $A$s and gives
\begin{equation}
\tan ^2 (\frac{1}{2} kL ) = \lambda^2 
\end{equation}
Hence
\begin{equation}
 \frac{kL}{2} = \pm \theta + n \pi \implies  k = \frac{2\pi}{L}( n \pm \frac{\theta}{\pi} )  \quad \theta \in [0,\frac{\pi}{2} ]  
\end{equation}
The normalized eigenfunctions are
\begin{equation}
f_n(x) = \sqrt{\frac{2}{L}}
\left\lbrace
\begin{aligned}
  \cos(kx +\frac{1}{2}kL ) &  \quad x < 0  \\
  \pm \sin(kx - \frac{1}{2}kL ) & \quad x > 0   \\
\end{aligned} \right. 
\qquad 
k = \frac{2\pi}{L}( n \pm  \frac{\theta}{\pi} )  \quad n \in \mathbb{Z} 
\end{equation}

{\bf Mode Expansion and Casimir Energy}:

Expand the field $\phi = \sum_n \phi_n f_n(x) $, the action and Hamiltonian becomes
\begin{equation}
  S = \frac{g}{2} \int dt \, \sum_{n \in \mathbb{Z} }\left(  \dot{\phi}^2_n + k^2 \phi_n^2 \right) \implies\quad   g \dot{\phi}_n  = \pi_n \quad \implies H =  
\frac{1}{2g}\sum_{n \in \mathbb{Z} } \pi_n^2 + ( kg )^2  \phi_n^2 
\end{equation}
Define the creation and annihilation operators as usual
\begin{equation}
\begin{aligned}
a_n = \frac{1}{\sqrt{2}} ( \sqrt{ |k|g} \phi_n + \frac{i }{\sqrt{|k|g} }\pi_n  ) \\
a^{\dagger}_n = \frac{1}{\sqrt{2}} ( \sqrt{ |k|g} \phi_n - \frac{i }{\sqrt{|k|g} }\pi_n  ) \\
\end{aligned}
\end{equation}
then
\begin{equation}
H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  (a^{\dagger}_n a_n + \frac{1}{2} )
\end{equation}
The Casimir energy is 
\begin{equation}
\begin{aligned}
E_c &= \frac{1}{4} \sum_{n \in \mathbb{Z}} | k| = \frac{\pi}{2L} ( \sum_{n \in \mathbb{Z}}  | n + x | + \sum_{n \in \mathbb{Z}}  | n - x |  )  = \frac{\pi}{L} ( \sum_{n \in \mathbb{Z}}  | n + x |  )\quad x = \frac{\theta}{\pi}\\  
&= \frac{\pi}{L} \Big[\sum_{n \ge 0 } ( n + x )^{-s} + \sum_{n \ge 0 }  ( n - x)^{-s}  +   x^{-s} \Big]\Big|_{s = -1} \\
&= \frac{\pi}{L} \left[ \zeta_{\rm H}( -1, x ) + \zeta_{\rm H}( -1, x ) +  x \right] \\
&= \frac{\pi}{L} ( - x^2 + x - \frac{1}{6})  = \frac{1}{2} ( - x^2 + x - \frac{1}{6})
\end{aligned}
\end{equation}
The free energy is
\begin{equation}
F = \frac{\beta}{2} ( - x^2 + x - \frac{1}{6}) = - \frac{\beta}{2} B_2( x) 
\end{equation}
The full expression also agrees with the boundary state calculation in Eq.~\ref{eq:dn_lambda_bd_state}

>>>>

\begin{figure}[h]
\centering
\includegraphics{fig_gnd_dn_lambda.pdf}
\caption{Partition function of Hamiltonian with DN and $\lambda$ boundary conditions. The width of the strip is $\pi$ due to folding. We unfold the cylinder and the new stripe have $N$ and $D$ boundary conditions on the left and right plus a $\lambda$ junction in the middle. }
\label{Fig in gnd_dn_lambda}
\end{figure}

In this appendix, we would like to calculate the amplitude for the setup shown in Fig.\ref{Fig in gnd_dn_lambda}. In particular, the unfolded configuration has D/N boundary conditions at $x = \pm \frac{L}{2}$ and linking boundary condition at $x = 0$. The general solutions can be written as
\begin{equation}
\label{Normalized f in gnd_dn_lambda}
f(k, x) = 
\left\lbrace
\begin{aligned}
  A_1 e^{i kt} \cos(kx +\frac{1}{2}kL ) &  \quad x < 0  \\
  A_2 e^{ikt}  \sin(kx - \frac{1}{2}kL ) & \quad x > 0   \\
\end{aligned} \right. 
\end{equation}
As demonstrated in the {\bf\color{red}main text}, if we denote $f(k,x<0)\equiv\phi_1$ and $f(k,x>0)\equiv\phi_2$, the boundary condition at the junction reads
\begin{eqnarray}\begin{aligned}
\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2} = \tan^2 \theta\frac{\partial_x \phi_2}{ \partial_t \phi_2} \quad \theta \in [0,\frac{\pi}{2} ]  
\end{aligned}\end{eqnarray}
which implies
\begin{equation}
\label{Momentum in gnd_dn_lambda}
k = \frac{2\pi}{L}( n \pm \frac{\theta}{\pi} )  \quad n\in{\bf Z}
\end{equation}
It is evident that the momentum $k$ is shifted from integer multiple of $2\pi/L$ due to the $\lambda$ boundary condition in the middle. 
\begin{comment}
Thus, the normalized eigenfunctions are
\begin{equation}
f_n(x) = \sqrt{\frac{2}{L}}
\left\lbrace
\begin{aligned}
  \cos(kx +\frac{1}{2}kL ) &  \quad x < 0  \\
  \pm \sin(kx - \frac{1}{2}kL ) & \quad x > 0   \\
\end{aligned} \right. 
\qquad 
k = \frac{2\pi}{L}( n \pm  \frac{\theta}{\pi} )  \quad n \in \mathbb{Z} 
\end{equation}
Expand the field $\phi = \sum_n \phi_n f_n(x) $, the action and Hamiltonian becomes
\begin{equation}
  S = \frac{g}{2} \int dt \, \sum_{n \in \mathbb{Z} }\left(  \dot{\phi}^2_n + k^2 \phi_n^2 \right) \implies\quad   g \dot{\phi}_n  = \pi_n \quad \implies H =  
\frac{1}{2g}\sum_{n \in \mathbb{Z} } \pi_n^2 + ( kg )^2  \phi_n^2 
\end{equation}
\end{comment}

It is clear that the normalized eigenfunctions in Eq.(\ref{Normalized f in gnd_dn_lambda}) serves as orthonormal basis in mode expansion. Follow the same procedure in {\bf\color{red}citeDiFrancesco}, we have the Hamiltonian as
\begin{equation}
\label{H in gnd_dn_lambda}
H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  (a^{\dagger}_n a_n + \frac{1}{2} )
\end{equation}
where the momentum $k$ is defined in Eq.(\ref{Momentum in gnd_dn_lambda}), and the creation and annihilation operators defined as usual
\begin{equation}
\begin{aligned}
a_n = \frac{1}{\sqrt{2}} ( \sqrt{ |k|g} \phi_n + \frac{i }{\sqrt{|k|g} }\pi_n  ) \\
a^{\dagger}_n = \frac{1}{\sqrt{2}} ( \sqrt{ |k|g} \phi_n - \frac{i }{\sqrt{|k|g} }\pi_n  ) \\
\end{aligned}
\end{equation}

The Casimir energy is the vacuum energy brought by the finite size of the setup. From Eq.(\ref{H in gnd_dn_lambda}) and define $x\equiv\theta/\pi$ in Eq.(\ref{Momentum in gnd_dn_lambda}), we have
\begin{equation}
\begin{aligned}
E_c &= \frac{1}{4} \sum_{n \in \mathbb{Z}} | k| = \frac{\pi}{2L} ( \sum_{n \in \mathbb{Z}}  | n + x | + \sum_{n \in \mathbb{Z}}  | n - x |  ) \\  
&= \frac{\pi}{L} \Big[\sum_{n \ge 0 } ( n + x )^{-s} + \sum_{n \ge 0 }  ( n - x)^{-s}  +   x^{-s} \Big]\Big|_{s = -1} \\
&= \frac{\pi}{L} \left[ \zeta_{\rm H}( -1, x ) + \zeta_{\rm H}( -1, x ) +  x \right] \\
&= \frac{1}{2} ( - x^2 + x - \frac{1}{6})
\end{aligned}
\end{equation}
where we used the fact that the unfolded geometry has length $L=2\pi$. Thus the free energy reads
\begin{equation}
F = \beta E_c = - \frac{\beta}{2} B_2( x) 
\end{equation}
{\bf\color{red}which agrees with the boundary state calculation in Eq.~\ref{eq:dn_lambda_bd_state}}
